Kid tangrams joint analysis

### 2025-10-30 code/ms_analysis.Rmd
double checking standardization of description , typo catches

transcripts |>
  filter(!is.na(trial)) |>
  filter(!is.na(role)) |>
  select(game, expt, trial, speaker_transcript = speaker, role, text) |>
  filter(role == "S") |>
  full_join(joint_demog) |>
  filter(speaker != speaker_transcript) |>
  select(expt, game, trial, text, speaker_transcript, speaker, listener)
```

>>>>

transcripts |>
  filter(!is.na(trial)) |>
  filter(!is.na(role)) |>
  select(game, expt, trial, speaker_transcript = speaker, role, text) |>
  filter(role == "S") |>
  full_join(joint_demog) |>
  filter(speaker != speaker_transcript) |>
  select(expt, game, trial, text, speaker_transcript, speaker, listener)

transcripts  |> filter(on_topic=="Y") |> filter(role=="S")|> select(expt, game, trial, text, description) |> View()
```
